---
title: "GSS challange"
author: "Kelly Patrizio!"
date: "October 8,2020"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)
GSS <-read.csv(file="GSScsv.csv",header=TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

Is belief in the bigbang theory (BIGBANG) independent of belief in an afterlife (POSTLIFE)?

$H_0$ The Null Hypothesis is that there is no relationship between the belief in the (BIGBANG) theory and belief in the afterlife (POSTLIFE).  

$H_A$  The Alternative Hypothesis is that there is a relationship between belief in the (BIGBANG) theory and belief in the afterlife (POSTLIFE).  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

```{r}
barchartGC(~BIGBANG + POSTLIFE,data=GSS)
barchartGC(~BIGBANG + POSTLIFE,data=GSS, type="percent")

```

In the above Bar Plot we see that approx. 8%  who do not believe in the BIGBANG Theory do not believe in POSTLIFE, and approx. 91% who do not believe in the BIGBANG Theory do believe in POSTLIFE.  We also can see that approx. 18% of those who do believe in the BIGBANG Theory do not believe in POSTLIFE, and that approx. 81% of those who do believe in the BIGBANG Theory do believe in POSTLIFE.  

### Numerical Descriptive Results


<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
table1 <- xtabs(~BIGBANG + POSTLIFE, data=GSS)
rowPerc(table1)
colPerc(table1)
```

In the above Numerical Cross-tab Graph above, we can see that out of 100 polled who don't believe in the BIGBANG Theory, 8% do not believe in POSTLIFE, and 18% of those who do believe in the BIGBANG Theory 82% believe in POSTLIFE.  In the second table, we can see that out of 100 who do not believe in a POSTLIFE, 35% do not believe in the BIGBANG Theory, and 57% who do believe in a POSTLIFE, 43% do believe in the BIGBANG Theory.  This does not appear to show a significant difference.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisher.test(table1)
```

Lastly to get an even clearer analysis, we ran a Fisher's Exact Test for Count Data above, that shows a p-value of more than 0.05 at 0.07143 which tells us that it is possible that there could be a relationship between the belief of the BIGBANG Theory and the belief in POSTLIFE.  

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variables causes the other, or whether they perhaps are related for some other reason.  Watch the chapter 6 videos from the George Town videos collection.!-->

In conclusion we fail to reject the Null Hypothesis due to lack of evidence to show a relationship between the two beliefs, BIGBANG Theory and POSTLIFE!
